Queue Aware Precoder Design for Space Frequency Resource Allocation

### 2014-07-01 Report/joint_wsrm_formulation.tex
Updated ver_1

The \ac{WSRM} technique is predominantly used to design the precoders for the \ac{MIMO} \ac{BC} channels to maximize the weighted sum throughput in the downlink direction. The weights are used to provide different priorities to the users based on their requirements and \ac{QoS} criterion. Since the objective of this work is mainly concerned with the reduction of the number of queued packets, we use the length of the queued packets for each user as the respective weights. Using the length of the queued packets as the corresponding weights is obtained from the well known algorithm, called the \textit{backpreassure algorithm}, which is used to decide the routing decisions for each node in the network to efficiently send the packets to the desired destination with minimal packet drops and delay. The backpreassure algorithm is the outcome of minimizing the Lyapunov drift conditioned over the current queue states \me{\mbf{Q}(i - 1)}, where \me{\mbf{Q}} is the vector formed by stacking the number of queued packets of each user in the system. Assuming the queue length grows according to \eqref{eqn-2a} for all the users, the Lyapunov drift conditioned over different channel realizations is given by \cite{georgiadis2006resource,neely2010stochastic}
\begin{equation} \label{eqn-3.1.0}
\Delta(i) = \frac{1}{2} \, \sum_{k \in \mc{U}} \, \mathrm{E}_H \Big{[}  \left ( Q_k(i)^2 - Q_k(i-1)^2 \right ) \vert \, \mbf{Q}(i - 1) \Big{]}.
\end{equation}
Now, by substituting \eqref{eqn-2a} in \eqref{eqn-3.1.0}, the resulting expression can be upper bounded by
\begin{equation}
\Delta(i)\leq \mathrm{E}_H \Big{[} \mbf{Q}(i-1) \left \lbrace \mbfa{\lambda}(i) - \mbf{t}(i) \right \rbrace | \mbf{Q}(i-1) \Big{]} + \mathrm{E}_H \left [ \mbfa{\lambda}^2(i-1) \right ] + \mathrm{E}_H \left [ \mbf{t}^2(i-1) \right ],
\end{equation}
where \me{\mbfa{\lambda}} and \me{\mbf{t}} are the stacked arrivals and transmissions of all users. Since the expectation is conditioned over \me{\mbf{Q}(i-1)} and the second order statistics of the arrivals and the transmissions are bounded \cite{neely2010stochastic}, the drift minimization solution is given as
\begin{equation}
\underset{\mbf{t}(i)}{\text{minimize}} \sum_{k \in \mc{U}} \, Q_k(i-1) \: t_k(i).
\label{backpreassure}
\end{equation}

Now from \eqref{backpreassure}, the optimization variables \me{\mbf{t}(i)}, which is the vectorized transmission rates, are to be identified for each user for the current slot \me{i}. Since the current system can exploit both space and frequency resources through \ac{MIMO} \ac{OFDM} model, the transmission rates \me{\mbf{t}(i)} for the current instant can be controlled using the transmit precoders \me{\mbf{M}_{k,n}} designed for each user over each sub-channel resource. Since the decision variables \me{\mbf{t}(i)} depends on the queue state at \me{\mbf{Q}(i - 1)}, we drop the time variable \me{i} for the easy representation. The above problem defined in \eqref{backpreassure} can be rewritten to include the space-frequency allocation variable, namely \me{\mbf{M}_{k,n}}, as
\begin{IEEEeqnarray}{rCl} \label{q_gen_sum}
\underset{\substack{\mvec{M}{k,n},\gamma_{l,k,n} \\ t_{l,k,n}}}{\text{maximize}} &\quad& \sum_{k \in \mc{U}} \, Q_k \left ( \sum_{n = 1}^N \sum_{l=1}^L t_{l,k,n} \right ) \IEEEyessubnumber \label{eqn-3.1.1} \\
\text{subject to.} & \quad & t_{l,k,n} \leq \log_2(1+\gamma_{l,k,n}) \IEEEyessubnumber \label{eqn-3.1.2} \\
& \quad &\sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \text{tr} \, (\mvec{M}{k,n} \mvec{M}{k,n}^\herm) \leq P_{{\max}}, \fall b, \IEEEyessubnumber \label{eqn-3.1.3} \\
& \quad & \sum_{n=1}^N \sum_{l = 1}^L t_{l,k,n} \leq Q_k, \fall k \in \mc{U} \IEEEyessubnumber \label{eqn-3.1.4}
\end{IEEEeqnarray}
where \eqref{eqn-3.1.4} is due to the \me{[x]^+} operation in \eqref{eqn-2a} and \me{\gamma_{l,k,n}} is defined in \eqref{eq:SINR}. By using the number of queued packets as the weights, the resources can be allocated to the user with the more number of backlogged packets, which essentially does the allocation in a greedy manner. As a special case of the problem defined in \eqref{q_gen_sum}, we can formulate the sum rate maximization problem by setting the weights in \eqref{eqn-3.1.1} as unity, leading to the problem as
\begin{IEEEeqnarray}{rCl}\label{gen_sum}
\underset{\substack{\mvec{M}{k,n},\gamma_{l,k,n} \\ t_{l,k,n}}}{\text{maximize}} &\quad& \sum_{k \in \mc{U}} \, \sum_{n = 1}^N \sum_{l=1}^L t_{l,k,n} \IEEEyessubnumber \\
\text{subject to.} & \quad & \eqref{eqn-3.1.1}, \eqref{eqn-3.1.2}, \eqref{eqn-3.1.3} \; \text{and} \; \eqref{eqn-3.1.4}. \IEEEyessubnumber
\end{IEEEeqnarray}

The problem defined in \eqref{gen_sum} provides an efficient queue minimizing approach as compared to \eqref{q_gen_sum}, since the resource allocation is driven by the channel conditions as compared to the number of queued packets in the problem defined in \eqref{q_gen_sum}. In both formulations, the resources allocated to the users are limited by the backlogged packets \eqref{eqn-3.1.4}, thereby handling the problem of over allocation. The resource allocation constraint in \eqref{eqn-3.1.4} renders the problem difficult to be solved by the iterative algorithm to design the precoders, which will be discussed later.

>>>>

The \ac{WSRM} technique is predominantly used to design the precoders for the \ac{MIMO} \ac{BC} channels to maximize the weighted sum throughput in the downlink direction. The weights are used to provide different priorities to the users based on their requirements and \ac{QoS} criterion. Since the objective of this work is mainly concerned with the reduction of the number of queued packets, we use the length of the queued packets for each user as the respective weights. Using the length of the queued packets as the corresponding weights is obtained from the well known algorithm, called the \textit{backpreassure algorithm}, which is used to decide the routing decisions for each node in the network to efficiently send the packets to the desired destination with minimal packet drops and delay. The backpreassure algorithm is the outcome of minimizing the Lyapunov drift conditioned over the current queue states \me{\mbf{Q}(i - 1)}, where \me{\mbf{Q}} is the vector formed by stacking the number of queued packets of each user in the system. Assuming the queue length grows according to \eqref{eqn-2a} for all the users, the Lyapunov drift conditioned over different channel realizations is given by
\begin{equation} \label{eqn-3.1.0}
\Delta(i) = \frac{1}{2} \, \sum_{k \in \mc{U}} \, \mathrm{E} \Big{[}  \left ( Q_k(i)^2 - Q_k(i-1)^2 \right ) \vert \, \mbf{Q}(i - 1) \Big{]},
\end{equation}
where the expectation is taken over all possible control decisions made in accordance to the channel under consideration to minimize the total backlogged packets at a given instant. Now, by substituting \eqref{eqn-2a} in \eqref{eqn-3.1.0}, the resulting expression is given by
\begin{equation}
\Delta(i) \leq \mathrm{E} \Big{[} \mbf{Q}(i-1) \left \lbrace \mbfa{\lambda}(i) - \mbf{t}(i) \right \rbrace | \mbf{Q}(i-1) \Big{]} + \frac{1}{2} \,\mathrm{E} \left [ \mbfa{\lambda}^2(i) | \mbf{Q}(i-1) \right ] + \frac{1}{2} \,\mathrm{E} \left [ \mbf{t}^2(i) | \mbf{Q}(i-1) \right ],
\label{drift-exp}
\end{equation}
where \me{\mbfa{\lambda}} and \me{\mbf{t}} are the vectors formed by stacking the arrival and transmission of all users in the system and the inequality is due to the upper bound\footnote{\me{\left ( \max{\Big [ \mbf{Q}(i-1) - \mbf{t}(i),0 \Big ] } + \mbfa{\lambda}(i) \right )^2 \leq \mbf{Q}^2(i-1) + \mbf{t}^2(i) + \mbfa{\lambda}^2(i) + 2 \, \mbf{Q}(i-1) \left ( \mbfa{\lambda}(i) - \mbf{t}(i) \right ) }}.

The first term in \eqref{drift-exp} can be neglected from the optimization, since the arrivals are independent of the current queue state following \me{\mathrm{E} [ \mbf{Q}(i-1) \mbfa{\lambda}(i) | \mbf{Q}(i-1)] = \mbf{Q}(i-1)\mathrm{E} [\mbfa{\lambda}(i)] = \mbf{Q}(i-1)\mbf{A}(i)}. In the backpreassure algorithm, discussed in \cite{georgiadis2006resource,neely2010stochastic}, the second order terms are bounded by a constant \me{B}, \textit{i.e}, \me{\mathrm{E} \left [ \mbfa{\lambda}^2(i) | \mbf{Q}(i-1) \right ] + \mathrm{E} \left [ \mbf{t}^2(i) | \mbf{Q}(i-1) \right ] \leq B}. With this approximation, the resulting problem can be represented as
\begin{equation}
\underset{\mbf{t}(i)}{\text{minimize}} \sum_{k \in \mc{U}} \, Q_k(i-1) \: t_k(i).
\label{backpreassure}
\end{equation}
In \eqref{backpreassure}, the expectation operator is dropped since it is maximized by maximizing the function inside it. Now from \eqref{backpreassure}, the optimization variables \me{\mbf{t}(i)}, which is the vectorized transmission rates, are to be identified for each user for the current slot \me{i}. Since the current system can exploit both space and frequency resources through \ac{MIMO} \ac{OFDM} model, the transmission rates \me{\mbf{t}(i)} for the current instant can be controlled using the transmit precoders \me{\mbf{M}_{k,n}} designed for each user over each sub-channel resource. Since the decision variables \me{\mbf{t}(i)} depends on the queue state at \me{\mbf{Q}(i - 1)}, we drop the time variable \me{i} for the easy representation. The above problem defined in \eqref{backpreassure} can be rewritten to include the space-frequency allocation variable, namely \me{\mbf{M}_{k,n}}, as
\begin{IEEEeqnarray}{rCl} \label{q_gen_sum}
\underset{\substack{\mvec{M}{k,n},\gamma_{l,k,n} \\ t_{l,k,n}}}{\text{maximize}} &\quad& \sum_{k \in \mc{U}} \, Q_k \left ( \sum_{n = 1}^N \sum_{l=1}^L t_{l,k,n} \right ) \IEEEyessubnumber \label{eqn-3.1.1} \\
\text{subject to.} & \quad & t_{l,k,n} \leq \log_2(1+\gamma_{l,k,n}) \IEEEyessubnumber \label{eqn-3.1.2} \\
& \quad &\sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \text{tr} \, (\mvec{M}{k,n} \mvec{M}{k,n}^\herm) \leq P_{{\max}}, \fall b, \IEEEyessubnumber \label{eqn-3.1.3} \\
& \quad & \sum_{n=1}^N \sum_{l = 1}^L t_{l,k,n} \leq Q_k, \fall k \in \mc{U} \IEEEyessubnumber \label{eqn-3.1.4}
\end{IEEEeqnarray}
where \eqref{eqn-3.1.4} is due to the \me{[x]^+} operation in \eqref{eqn-2a} and \me{\gamma_{l,k,n}} is defined in \eqref{eq:SINR}. By using the number of queued packets as the weights, the resources can be allocated to the user with the more number of backlogged packets, which essentially does the allocation in a greedy manner. As a special case of the problem defined in \eqref{q_gen_sum}, we can formulate the sum rate maximization problem by setting the weights in \eqref{eqn-3.1.1} as unity, leading to the problem as
\begin{IEEEeqnarray}{rCl}\label{gen_sum}
\underset{\substack{\mvec{M}{k,n},\gamma_{l,k,n} \\ t_{l,k,n}}}{\text{maximize}} &\quad& \sum_{k \in \mc{U}} \, \sum_{n = 1}^N \sum_{l=1}^L t_{l,k,n} \IEEEyessubnumber \\
\text{subject to.} & \quad & \eqref{eqn-3.1.1}, \eqref{eqn-3.1.2}, \eqref{eqn-3.1.3} \; \text{and} \; \eqref{eqn-3.1.4}. \IEEEyessubnumber
\end{IEEEeqnarray}

The problem defined in \eqref{gen_sum} provides an efficient queue minimizing approach as compared to \eqref{q_gen_sum}, since the resource allocation is driven by the channel conditions as compared to the number of queued packets as in \eqref{q_gen_sum}. It is to be noted that in both formulations, the resources allocated to the users are limited by the backlogged packets \eqref{eqn-3.1.4}, thereby handling the problem of over allocation explicitly with an additional rate constraint.

### 2014-07-01 Report/mse_formulation.tex
Updated ver_1

In this section, we provide an alternative formulation for the \ac{QM} \ac{JSFRA} scheme using the \ac{MSE} equivalence with the capacity as in \cite{wmmse_shi,kaleva2012weighted} for the \ac{WSRM} problem. The proposed formulation uses the well known relation between the capacity and the \ac{MSE} given by \me{C(\gamma) = \log_2 \left ( {1}/{\epsilon} \right )}, where \me{\epsilon = {1} / {(1 + \gamma)}} is the \ac{MSE} expression for decoding the transmitted symbols using \ac{MMSE} receivers and \me{C} being the capacity of the system. Using the \ac{MSE} relation, \eqref{eqn-6} is written as
\begin{IEEEeqnarray}{rCl}\label{eqn-mse-1}
\text{minimize} &\quad& \|  \tilde{\mbf{v}}  \|_q \IEEEyessubnumber \label{eqn-mse-1.1} \\
\text{subject to} & \quad & t_{l,k,n} \leq -\log_2(\epsilon_{l,k,n}), \IEEEyessubnumber \label{eqn-mse-1.2} \\
& \quad & \epsilon_{l,k,n} \geq  \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{(j,i) \neq (l,k)} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,i,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2 \IEEEyessubnumber \label{eqn-mse-1.3} \\
&\quad& \text{and} \; \eqref{eqn-4.3},  \IEEEyessubnumber \label{eqn-mse-1.4}
\end{IEEEeqnarray}
where \eqref{eqn-mse-1.3} bounds the \ac{MSE} by \me{\epsilon_{l,k,n}} and \eqref{eqn-mse-1.2} relaxes the transmitted rate \me{\mvec{t}{l,k,n}} using the the \ac{MSE} relation.

@@

Now, using the above approximation for the rate constraint, the optimization problem is solved for the optimal precoders \me{\mvec{m}{l,k,n}}, \acp{MSE} \me{\epsilon_{l,k,n}} and the users rates over each sub-channel \me{t_{l,n,k}}. Once the optimal values are available, the local \ac{MSE} value \me{\tilde{\epsilon}_{l,k,n}} is now updated with the new value \me{\epsilon_{l,k,n}}. The optimization problem can be given as
\begin{IEEEeqnarray}{rCl}\label{eqn-mse-2}
\text{minimize} &\quad& \|  \tilde{\mbf{v}}  \|_q \IEEEyessubnumber \label{eqn-mse-2.1} \\
\text{subject to} & \quad & \eqref{eqn-4.3}, \: \eqref{mse-lin}  \IEEEyessubnumber \label{eqn-mse-2.2} \\
& \quad & \epsilon_{l,k,n} \geq  \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{(j,i) \neq (l,k)} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,i,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2 \IEEEyessubnumber \label{eqn-mse-2.3}.
\end{IEEEeqnarray}
The algorithmic representation is similar to Algorithm \ref{algo-1}, with \eqref{eqn-9} is replaced by \eqref{eqn-mse-2}. The convergence of the \ac{MSE} reformulation algorithm follows the similar comments drawn in \cite{christensen2008weighted,wmmse_shi}. Since at each \ac{KKT} point, the gradient of the original problem and the \ac{MSE} reformulation problem are made equal by the weights in the \ac{MSE} reformulation, the problem is guaranteed to converge to the optimal solution by following the same stationary \ac{KKT} points.

>>>>

In this section, we provide an alternative formulation for the \ac{QM} \ac{JSFRA} scheme using the \ac{MSE} equivalence with the capacity as in \cite{wmmse_shi,kaleva2012weighted} for the \ac{WSRM} problem. The proposed formulation uses the well known relation between the capacity and the \ac{MSE} given by \me{C(\gamma) = \log_2 \left ( {1}/{\epsilon} \right )}, where \me{\epsilon = {1} / {(1 + \gamma)}} is the \ac{MSE} expression for decoding the transmitted symbols using \ac{MMSE} receivers and \me{C} being the capacity of the system. Let \me{{v}^{\prime}_k = Q_k - \sum_{n=1}^N \sum_{l=1}^L t_{l,k,n}} denotes the queue deviation corresponding to the user \me{k} and \me{\tilde{{v}}^{\prime}_k \triangleq a_k^{1/{q}}v^{\prime}_k} represents the weighted equivalent. Now, using the \ac{MSE} relation, \eqref{eqn-6} is written as
\begin{IEEEeqnarray}{rCl}\label{eqn-mse-1}
\underset{\substack{t_{l,k,n},\mvec{m}{l,k,n},\\\epsilon_{l,k,n},\mvec{w}{l,k,n}}}{\text{minimize}} &\quad& \|  \tilde{\mbf{v}}^{\prime}  \|_q \IEEEyessubnumber \label{eqn-mse-1.1} \\
\text{subject to} & \quad & t_{l,k,n} \leq -\log_2(\epsilon_{l,k,n}), \IEEEyessubnumber \label{eqn-mse-1.2} \\
& \quad & \epsilon_{l,k,n} \geq  \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{(j,i) \neq (l,k)} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,i,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2 \IEEEyessubnumber \label{eqn-mse-1.3} \\
&\quad& \text{and} \; \eqref{eqn-4.3},  \IEEEyessubnumber \label{eqn-mse-1.4}
\end{IEEEeqnarray}
where \eqref{eqn-mse-1.3} bounds the \ac{MSE} by \me{\epsilon_{l,k,n}} and \eqref{eqn-mse-1.2} relaxes the transmitted rate \me{{t}_{l,k,n}} using the the \ac{MSE} relation.

@@

Now, using the above approximation for the rate constraint, the optimization problem is solved for the optimal precoders \me{\mvec{m}{l,k,n}}, \acp{MSE} \me{\epsilon_{l,k,n}} and the users rates over each sub-channel \me{t_{l,n,k}}. Once the optimal values are available, the local \ac{MSE} value \me{\tilde{\epsilon}_{l,k,n}} is now updated with the new value \me{\epsilon_{l,k,n}}. The optimization problem can be given as
\begin{IEEEeqnarray}{rCl}\label{eqn-mse-2}
\underset{\substack{t_{l,k,n},\mvec{m}{l,k,n},\\\epsilon_{l,k,n},\mvec{w}{l,k,n}}}{\text{minimize}} &\quad& \|  \tilde{\mbf{v}}^{\prime}  \|_q \IEEEyessubnumber \label{eqn-mse-2.1} \\
\text{subject to} & \quad & \eqref{eqn-4.3}, \: \eqref{mse-lin}  \IEEEyessubnumber \label{eqn-mse-2.2} \\
& \quad & \epsilon_{l,k,n} \geq  \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{(j,i) \neq (l,k)} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,i,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2 \IEEEyessubnumber \label{eqn-mse-2.3}.
\end{IEEEeqnarray}

\subsubsection*{Convergence}
The convergence of the \ac{MSE} reformulation algorithm follows the similar comments drawn in \cite{christensen2008weighted,wmmse_shi}. Since at each \ac{KKT} point, the gradient of the original problem and the \ac{MSE} reformulation problem are made equal by the weights used in the \ac{MSE} reformulation, the problem is guaranteed to converge to the optimal solution by following the same stationary \ac{KKT} points.

### 2014-07-01 Report/problem_formulation.tex
Updated ver_1

In order to minimize the number of queued packets at the \acp{BS}, the precoders \me{\mbf{M}_{k,n}} are designed to distribute the resources in an efficient manner to the users by utilizing both spatial and frequency dimension. The problem defined in \eqref{q_gen_sum} raises a question, namely, the linearity of the weights used in the objective function. It can also be a quadratic function, providing more emphasis on the users with large number queued packets as compared to the users with the small queue sizes or some other function of \me{\mbf{Q}}. In order to answer this question, we discuss the \ac{JSFRA} problem formulation, which restricts the solution only to the power functions. For practical and tractability reasons, we impose a constraint that the maximum number of transmitted bits for the user \me{k} is limited by the packets available at the transmitter. As a result, the number of backlogged packets remaining in the system is given by
\begin{equation}
v_k =  Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} \log_2(1+\gamma_{l,k,n}) \geq 0 \fall k \in \mathcal{U}.
\label{eqn-4.2}
\end{equation}

The precoder design problem can be given minimizing the absolute value of the deviation in \eqref{eqn-4.2} raised to the exponent \me{q} as
\me{\text{minimize} \: \sum_{k \in \mc{U}} \, | v_k |^q}. The exponent \me{q} plays a vital role in the final allocation, which will be discussed later. Now, the problem of weighted queued packet minimization formulated as a $q$-norm minimization, is given by
\begin{IEEEeqnarray}{rCl}\label{eqn-3}
\underset{\substack{\mvec{m}{l,k,n},\\\mvec{w}{l,k,n}}}{\text{minimize}} &\quad& \|  \tilde{\mbf{v}}  \|_q\IEEEyessubnumber \\
\text{subject to} & \quad&\sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \text{tr} \, (\mvec{M}{k,n} \mvec{M}{k,n}^\herm) \leq P_{{\max}}, \fall b, \IEEEyessubnumber \label{eqn-4.3}
\end{IEEEeqnarray}
where \me{\tilde{v}_k \triangleq a_k^{1/{q}}v_k}, \me{a_k} is the weighting factor which is incorporated to control user priority based on their respective \ac{QoS}, \me{\gamma_{l,k,n}} is defined in \eqref{eq:SINR}, and \me{\mbf{M}_{k,n} \triangleq [ \, \mvec{m}{1,k,n} \, \mvec{m}{2,k,n} \dotsc \mvec{m}{L,k,n} \,]} comprises the beamformers associated with the user \me{k} for \me{n^\mathrm{th}} sub-channel transmission. It can be easily extended for user specific streams \me{L_k} instead of using the common \me{L} streams for all users. The expression for \me{t_{l,k,n}} is due to the assumption of Gaussian signaling, so that the maximum achievable rate is \me{\log_2(1 + \gamma_{l,k,n})} for a given \ac{SINR} \me{\gamma_{l,k,n}}. In \eqref{eqn-4.3}, we consider the sum power constraint for each \ac{BS} across all sub-channels. The proposed solution presented in this section also applies to the sub-channel power constraint by replacing \eqref{eqn-4.3} by corresponding formulations. Before proceeding further, we note that the constraint in \eqref{eqn-4.2} is handled implicitly by the definition of the \me{q}-norm in the objective of \eqref{eqn-3}. As a proof, suppose that \me{t_k>Q_k} for a certain \me{k} at optimum, i.e., \me{-{v}_k=t_k-Q_k>0}. Then there exists \me{\delta_k>0} such that \me{-{v}^{\prime}_k=t^{\prime}_k-Q_k<-{v}_k} where \me{t^{\prime}_k=t_k-\delta_k}. Since \me{\|\tilde{\mbf{v}}\|_q=\| |\tilde{\mbf{v}}| \|_q=\||-\tilde{\mbf{v}}|\|_q}, this means that the newly created vector \me{\mbf{t}^{\prime}} achieves a smaller objective which contradicts with the fact that an optimal solution has been obtained. We comment on the choice of  the norm \me{q} on the objective as below \cite{berry2004cross,qps_cioffi}.
\begin{itemize}
\item With \me{q = 1}, the objective results in greedy allocation \textit{i.e}, emptying the queue of users with good channel condition before considering the users with worse channel conditions. As a special case, it is easy to see that \eqref{eqn-3} reduces to the \ac{Q-WSRM} problem \eqref{gen_sum} when the queue size is large enough for all users.
\item With \me{q = 2}, the objective prioritizes users with higher queued packets before considering the users with a smaller number of backlogged packets. This is ideal for the delay limited scenario when the packet arrival rates of the users are similar, since the backlogged packets is proportional to the delay in the transmission following the Little's law \cite{neely2010stochastic}.
\item With \(q = \infty \), the objective minimizes the maximum number of queued packets among users with the current transmission, thereby providing queue fairness by allocating the resources proportional to the number of backlogged packets.
\end{itemize}

>>>>

The problem defined in \eqref{q_gen_sum} ignores the second order term arising from the Lyapunov drift minimization objective by the limiting it to a constant term. It can be seen that \eqref{eqn-4.2} provides similar expression when the exponent is set to be \me{q=2} as
\begin{equation}\label{pf-1}
\underset{t_k}{\text{minimize}} \, \sum_k \, v_k^2 = \underset{t_k}{\text{minimize}} \, \sum_k \, Q_k^2 - 2 \, Q_k t_k + t_k^2.
\end{equation}
It can seen that \eqref{pf-1} is equivalent to the \eqref{backpreassure} algorithm when we ignore the second order terms from \eqref{pf-1}. It can be seen that by dropping the second order term from the \ac{Q-WSRM} formulation, we require an explicit rate constraint \eqref{eqn-3.1.4} to limit the allocations beyond the respective user requirements. In the current queue deviation formulation, the explicit rate constraint is not needed, since it is handled by the objective function itself. Since the objective is to minimize the number of queued packets, the sub-channels are coupled in this formulation as compared to the traditional \ac{WSRM} objective eventhough the interference from the adjacent sub-channels are zero (due to the \ac{OFDM} scheme). The queue deviation objective provides an alternate and more complete way to perform the resource allocation as compared to the \eqref{q_gen_sum} approach.

Before proceeding further, we note that the constraint in \eqref{eqn-4.2} is handled implicitly by the definition of the \me{q}-norm in the objective of \eqref{eqn-3}. As a proof, suppose that \me{t_k>Q_k} for a certain \me{k} at optimum, i.e., \me{-{v}_k=t_k-Q_k>0}. Then there exists \me{\delta_k>0} such that \me{-{v}^{\prime}_k=t^{\prime}_k-Q_k<-{v}_k} where \me{t^{\prime}_k=t_k-\delta_k}. Since \me{\|\tilde{\mbf{v}}\|_q=\| |\tilde{\mbf{v}}| \|_q=\||-\tilde{\mbf{v}}|\|_q}, this means that the newly created vector \me{\mbf{t}^{\prime}} achieves a smaller objective which contradicts with the fact that an optimal solution has been obtained. We comment on the choice of  the norm \me{q} on the objective as below \cite{berry2004cross,qps_cioffi}.
\begin{itemize}
\item With \me{q = 1}, the objective results in greedy allocation \textit{i.e}, emptying the queue of users with good channel condition before considering the users with worse channel conditions. As a special case, it is easy to see that \eqref{eqn-3} reduces to the \ac{WSRM} problem \eqref{gen_sum} when the queue size is large enough for all users.
\item With \me{q = 2}, the objective prioritizes users with higher number of queued packets before considering the users with a smaller number of backlogged packets. For example, it could be more ideal for the delay limited scenario when the packet arrival rates of the users are similar, since the backlogged packets is proportional to the delay in the transmission following the Little's law \cite{neely2010stochastic}.
\item With \(q = \infty \), the objective minimizes the maximum number of queued packets among users with the current transmission, thereby providing queue fairness by allocating the resources proportional to the number of backlogged packets.
\end{itemize}
